More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-07-09 2016-Weak-FH-Bisim/WeakBisim.tex
2eme essai
rewriting of proof Theorem 7

The semantics of open pNets will be defined  as an open automaton. An open
automaton is an automaton where each transition composes transitions of several LTSs with
action of some holes, the transition occurs if some predicates hold, and can involve a 
set of state modifications.
%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
%different 
%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
\begin{definition}[Open transitions]\label{def:OT}
	\label{def:OpenTransitions}
	An \emph{open transition} over a
	set $J$ of holes with sorts $\Sort_j^{j\in J}$ and a set of states $\mathcal{S}$ is 
	a structure of the form:	
	\begin{mathpar}
	\openrule
	{	\beta_j^{j\in J}, \Pred, \Post}
	{s \OTarrow {\alpha}s'}
	\end{mathpar}
	Where $s, s'\in\mathcal{S}$ and $\beta_j$
        is a transition of the hole $j$, with $\beta_j\in\Sort_j$. $\alpha$ is an action 
        label denoting the resulting action
        of this open transition. \Pred\ is a predicate 
	over the different variables of the
	terms, labels, and states $\beta_j$, $s$, $\alpha$. \Post\ is a set of 
	equations 
	that 
	hold \emph{after the open transition}, they are represented as a substitution of the 
	form $({x_k\gets e_k})^{k\in K}$ 
	where $x_k$ are variables of $s'$, and $e_k$ are expressions over the other 
	variables of the open transition. Open transitions are identified modulo logical equivalence on their predicate.
\end{definition}

@@

We define $\vis{\overline\beta}$ as the mapping $\overline\beta$  without  invisible actions but where each element is now a list (if length 1).\\ $\vis{\beta_i^{i\in I}} = [\beta_i]^{i\in I'}$ s.t. $I'=\left\{i| i\in I \land \beta_i\neq \tau\right\}$.
\begin{definition}[Weak open transition]\label{def:weakOT}
A weak open transition over a
	set $J$ of holes with sorts $\Sort_j^{j\in J}$ and a set of states $\mathcal{S}$ is 
	a structure of the form:	
\begin{mathpar}
 \openrule
         {
           \gamma_j^{j\in J'},\Pred,\Post}
         {s \OTWeakarrow {\alpha} s'}
 \end{mathpar}
	Where $J'\subseteq J$, $s, s'\in\mathcal{S}$ and $\gamma_j$
        is a list of transitions of the hole $j$, with each element of the list in $\Sort_j$. $\alpha$ is an action 
        label denoting the resulting action
        of this open transition. \Pred\ and \Post\ are defined similarly to Definition~\ref{def:OT}. We use $\WT$ to range over sets of weak open transitions.

@@

@@

We will show that $\mathcal{R}''$ is a weak FH-bisimulation. Consider 
$(s,u|\Pred_{s,u})\in\mathcal{R}''$. Then there is a set of states of $\mathcal{S}_3$ relating $s$ and $u$, let $(p)^{p\in \mathcal{S}_2}$ be this family.  We have $\Pred_{s,u} = \bigvee_{p\in \mathcal{S}_2} \Pred_{s,p}\land\Pred_{p,u}$.

@@

For any $p\in \mathcal{S}_2$ by definition of $\mathcal{R}''$, $(s,p|\Pred_{s,p})\in\mathcal{R}$,  and $(p,u|\Pred_{p,u})\in\mathcal{R}'$. 
We have the following by definition of weak bisimulation:\\
For any open transition $OT$ in $\mathcal{T}_1$ originating from $s$.
       	\begin{mathpar}
       	\openrule
       	{
       		\beta_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
       	{s \OTarrow {\alpha} {s}'}  \qquad (1)   	
       	\end{mathpar}

       	There exist weak open transitions $OT_{x}^{x\in X} \subseteq \mathcal{T}_2$:

       	\begin{mathpar} 
       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
       	\openrule
       	{
       		\gamma_{j x}^{j\in J_{x}}, \Pred_{OT_{x}},\Post_{OT_{x}}}
       	{p \OTWeakarrow {\alpha_{x}} p'_{x}}\qquad (2)
       	%         \right)
       	\end{mathpar}

       	such that  $\forall x, J_1=J_{x}, (s',p'_{x}|\Pred\,'_{{x}})\in 
       	\mathcal{R}$;
       	and  \\

       	$\Pred_{s,p} \land \Pred_{OT}\\
       	\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       	\left( \forall j. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_{x}}
       	\land \alpha\!=\!\alpha_{x} \land
       	\Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\right)$\\

For any open transition $OT_{x}$, since
       	$(p,u_x|\Pred_{x})\in\mathcal{R}'$ there exist open transitions
       	$OT_{xy}^{y\in Y} \subseteq \mathcal{T}_3$:

       	\begin{mathpar}  	
       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
       	\openrule
       	{
       		\gamma_{j  x y}^{j\in J_{xy}}, 
       		\Pred_{OT_{xy}},\Post_{OT_{xy}}}
       	{u \OTWeakarrow {\alpha_{xy}} u'_{xy}}\qquad (3)
       	%         \right)    	
       	\end{mathpar}
       	such that  $\forall y, J_{x}=J_{xy}, 
       	(p'_{x},u'_{xy}|\Pred\,'_{{x,xy}})\in \mathcal{R}'$; and  \\
       	$\Pred_{p,u} \land \Pred_{OT_{x}}\\
       	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
       	\left( \forall j. \gamma_{jx}=\gamma_{jxy}  \Rightarrow \Pred_{OT_{xy}}
       	\land \alpha_{x}\!=\!\alpha_{xy} \land
       	\Pred\,'_{{x,xy}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}}\right)$.\\

This is verified for all $p \in \mathcal{S}_2$. Overall,  we have a family of open 
       	transitions 
       	$OT_{xy}^{x\in X, 
       		y\in Y} \subseteq \mathcal{T}_3$ that should simulate \emph{OT}.

We have  $\forall y, \forall x,  J_1=J_{x}=J_{xy}, 
       	({s}',u'_{xy}|\Pred\,'_{{xy}})\in \mathcal{R}''$ for some $\Pred\,'_{{xy}}$.  Indeed,  for any $x$ and $y$, we have $p'_{x}$ relates ${s}'$ and $u'_{xy}$, indeed we have
$(s',p'_{x}|\Pred\,'_{{x}})\in \mathcal{R}$
       	and $(p'_{x},u'_{xy}|\Pred\,'_{{x,xy}})\in \mathcal{R}'$. For states ensuring the transitivity relation we have   
       		 for all  $x$, $y$, $\Pred\,'_{x}\land 
       	\Pred\,'_{{x,xy}}\implies 
       	\Pred\,'_{{xy}}$.

\TODO{We need to prove that we have the following  relation:}  \\     	
       	\begin{small}
 $\Pred_{s,u} \land \Pred_{OT}\\
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}
       		\left( \forall j. \vis{\beta_j}=\gamma_{jxy}  \Rightarrow \Pred_{OT_{xy}}
       		\land \alpha\!=\!\alpha_{xy} \land
       		\Pred\,'_{{xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{xy}}}\right)$.
       	\end{small}

\noindent By rule given in (2) we have for all state $p$:\\
\begin{small}
$\big(\Pred_{s,p} \land \Pred_{OT}\big)\land\Pred_{p,u}\\
       		\hspace{1cm} \implies\!\!\! \Big(\bigvee_{x\in X}
       		\left( \forall j. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_{x}}
       		\land \alpha\!=\!\alpha_{x} \land
       		\Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\right)\Big)\land\Pred_{p,u}\\
       		%
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       	\Big( \forall j. \vis{\beta_j}=\gamma_{jx}  \Rightarrow 
       		(\Pred_{OT_{x}}\land\Pred_{p,u})
       		\land \alpha\!=\!\alpha_{x} \land
       		\Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\Big).\\
       		%
       		$
  \end{small}

\noindent By rule given in (3) we get:     \\	
	\begin{small}
$    \big(\Pred_{s,p} \land \Pred_{OT}\big)\land\Pred_{p,u}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       		\bigg( \forall j. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Big(\bigvee_{y\in Y} 
       		\big( \forall j'.\gamma_{j'x}=\gamma_{j'xy}  \Rightarrow \Pred_{OT_{xy}}
       		\land \alpha_{x}\!=\!\alpha_{xy}\land\\
       		%
 \Pred\,'_{{x,xy}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}}\Big)
       		\land \alpha\!=\!\alpha_{x} \land
       \Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\bigg)\\
       		%
 \hspace{1cm} \implies\!\!\! \bigvee_{x\in X} \bigvee_{y\in Y}
       		\bigg(\forall j, j'.\vis{\beta_j}=\gamma_{jx} \land \gamma_{j'x}=\gamma_{j'xy}
       		\Rightarrow \Big( 
       		\Pred_{OT_{xy}}
       		\land \alpha\!=\alpha_{x}\!=\!\alpha_{xy} \land
       \Pred\,'_{{x,xy}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}}
       		\land
\Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\Big)\bigg).
       		$
       \end{small}

\medskip
\noindent Because of variables domains independence we  have:\\ 
    $\Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\land 
       	\Pred\,'_{{x,xy}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}}
       	\Leftrightarrow\\ % we changed =
\Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}}\land
       \Pred\,'_{{x,xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}} \Leftrightarrow
\big(\Pred\,'_{{x}} \land   \Pred\,'_{{x,xy}}\big)   \subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}} \\	\implies\Pred\,'_{{xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}}
   \Leftrightarrow  \Pred\,'_{{xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{xy}}} $\\

\noindent This allows us to conclude, with $\Pred_{s,u} = \bigvee_{p\in \mathcal{S}_2} 
       	\Pred_{s,p}\land\Pred_{p,u}$:

      	\begin{small}     	
$\Pred_{s,u} \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{p\in \mathcal{S}_2} \big(
	\Pred_{s,p}\land\Pred_{p,u}\big) \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\!\bigvee_{p\in \mathcal{S}_2}\bigg(\!\!
 \bigvee_{x\in X}\!\!\bigvee_{y\in Y}\!\!
\Big( \forall j, j'.\vis{\beta_j}=\gamma_{jx} \land \gamma_{j'x}=\gamma_{j'xy}
\Rightarrow \Big( 
\Pred_{OT_{xy}}
\land \alpha\!=\alpha_{x}\!=\!\alpha_{xy}\\~\hspace{3em}~ \land
\Pred\,'_{{xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{xy}}}\Big)\Big)\bigg)
\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\!\!\bigvee_{y\in Y}\!\!\bigvee_{p\in \mathcal{S}_2}\!\!
\Big(\forall j.\vis{\beta_j}\!=\!\gamma_{jxy}  \Rightarrow \Pred_{OT_{xy}}
\land\, \alpha\!=\!\alpha_{xy} \land
\Pred\,'_{{xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{xy}}}\Big)$.
  \end{small}

>>>>

The semantics of open pNets will be defined  as an open automaton. An open
automaton is an automaton where each transition composes transitions of several LTSs with
action of some holes, the transition occurs if some predicates hold, and can involve a 
set of state modifications.
%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
%different 
%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
\begin{definition}[Open transitions]\label{def:OT}
	\label{def:OpenTransitions}
	An \emph{open transition} over a
	set $J$ of holes with sorts $\Sort_j^{j\in J}$ and a set of states $\mathcal{S}$ is 
	a structure of the form:	
	\begin{mathpar}
	\openrule
	{	\beta_j^{j\in J'}, \Pred, \Post}
	{s \OTarrow {\alpha}s'}
	\end{mathpar}
	Where $J'\subseteq$, $s, s'\in\mathcal{S}$ and $\beta_j$
        is a transition of the hole $j$, with $\beta_j\in\Sort_j$. $\alpha$ is an action 
        label denoting the resulting action
        of this open transition. \Pred\ is a predicate 
	over the different variables of the
	terms, labels, and states $\beta_j$, $s$, $\alpha$. \Post\ is a set of 
	equations 
	that 
	hold \emph{after the open transition}, they are represented as a substitution of the 
	form $({x_k\gets e_k})^{k\in K}$ 
	where $x_k$ are variables of $s'$, and $e_k$ are expressions over the other 
	variables of the open transition. Open transitions are identified modulo logical equivalence on their predicate.
\end{definition}

@@

\begin{definition}[Weak open transition]\label{def:weakOT}
A weak open transition over a
	set $J$ of holes with sorts $\Sort_j^{j\in J}$ and a set of states $\mathcal{S}$ is 
	a structure of the form:	
\begin{mathpar}
 \openrule
         {
           \gamma_j^{j\in J'},\Pred,\Post}
         {s \OTWeakarrow {\alpha} s'}
 \end{mathpar}
	Where $J'\subseteq J$, $s, s'\in\mathcal{S}$ and $\gamma_j$
        is a list of transitions of the hole $j$, with each element of the list in $\Sort_j$. $\alpha$ is an action 
        label denoting the resulting action
        of this open transition. \Pred\ and \Post\ are defined similarly to Definition~\ref{def:OT}. We use $\WT$ to range over sets of weak open transitions.

@@

We define $\vis{\overline\beta}$ as the mapping $\overline\beta$  without  invisible actions but where each element is now a list (if length 1).\\ $\vis{\beta_i^{i\in I}} = [\beta_i]^{i\in I'}$ s.t. $I'=\left\{i| i\in I \land \beta_i\neq \tau\right\}$.

@@

---------------------------------------------------------------------

Consider 3 open automata 
       	$\mathcal{T}_1$, $\mathcal{T}_2$, $\mathcal{T}_3$ and states $s$, $t$, $u$ 
       	in those 
       	automata\footnote{We omit the constraints stating that each $s_x,\,t_x,\,u_x$ is 
       	in the 
       	states of 
       		$\mathcal{T}_1,\,\mathcal{T}_2,\,\mathcal{T}_3$ for the sake of readability}.
       	Suppose we have $\mathcal{R}$ an FH-bisimulation relation between states of 
       	$\mathcal{T}_1$ and of  $\mathcal{T}_2$; members of $\mathcal{R}$ are of the form 
       	$(s,t|\Pred_{s,t})$.
       	Suppose we also  have $\mathcal{R}'$ an FH-bisimulation relation between states 
       	of 
       	$\mathcal{T}_2$ and of  $\mathcal{T}_3$; members of $\mathcal{R}'$ are of the 
       	form 
       	$(t,u|\Pred_{t,u})$.

@@

       	For any $p\in P$ by definition of $\mathcal{R}''$,
       	$(s,t_p|\Pred_{s,p})\in\mathcal{R}$,  and 
       	$(t_p,u|\Pred\,'_{p,u})\in\mathcal{R}'$. 
       	We have 
       	the 
       	following by definition of bisimulation:
For any $p\in \mathcal{S}_2$ by definition of $\mathcal{R}''$, $(s,p|\Pred_{s,p})\in\mathcal{R}$,  and $(p,u|\Pred_{p,u})\in\mathcal{R}'$. 
We have the following by definition of weak bisimulation:\\
For any open transition $OT$ in $\mathcal{T}_1$ originating from $s$.
       	\begin{mathpar}
       	\openrule
       	{
       		\beta_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
       	{s \OTarrow {\alpha} {s}'}  \qquad (1)   	
       	\end{mathpar}

       	There exist weak open transitions $OT_{px}^{x\in X} \subseteq \mathcal{T}_2$:

       	\begin{mathpar} 
       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
       	\openrule
       	{
       		\gamma_{jpx}^{j\in J_{px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
       	{t \OTWeakarrow {\alpha_{px}} t_{px}}\qquad (2)
       	%         \right)
       	\end{mathpar}

       	such that  $\forall x, \{j\in J_1|\beta_j \neq \tau\}=J_{x}, (s',t_{px}|\Pred\,_{s'\!,{px}})\in 
       	\mathcal{R}$;
       	and  \\

       	$\Pred_{s,p} \land \Pred_{OT}\\
       	\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       	\left( \forall j. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_{px}}
       	\land \alpha\!=\!\alpha_{px} \land
       	\Pred\,_{s'\!,{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)$\\

       	\begin{mathpar}  	
       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
       	\openrule
       	{
       		\gamma_{jpxy}^{j\in J_{pxy}}, 
       		\Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
       	{u \OTWeakarrow {\alpha_{pxy}} u_{pxy}}\qquad (3)
       	%         \right)    	
       	\end{mathpar}
       	such that  $\forall y, J_{px}=J_{pxy}, 
       	(t_{px},u_{pxy}|\Pred_{{px,pxy}})\in \mathcal{R}'$; and  \\
       	$\Pred_{p,u} \land \Pred_{OT_{px}}\\
       	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
       	\left( \forall j. \gamma_{jpx}=\gamma_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
       	\land \alpha_{px}\!=\!\alpha_{pxy} \land
       	\Pred_{{px,pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$.\\

This is verified for all $p \in P$. Overall,  we have a family of open 
       	transitions 
       	$OT_{xy}^{p\in P, x\in X, 
       		y\in Y} \subseteq \mathcal{T}_3$ that should simulate \emph{OT}.

------------------------------------------------------------------

We have  $\forall y, \forall x, \forall p \in P,  \{j \in J_1|\,\beta_j\neq \tau\} =J_{px}=J_{pxy}, 
       	({s}',u_{pxy}|\Pred_{s',{pxy}})\in \mathcal{R}''$ for some $\Pred_{{s',pxy}}$.  Indeed,  for any $p$, $x$ and $y$,  we have
$(s',t_{px}|\Pred_{{s'\!,px}})\in \mathcal{R}$
       	and $(t_{px},u_{pxy}|\Pred_{{px,pxy}})\in \mathcal{R}'$. For states ensuring the transitivity relation we have   
       		 for all $p$, $x$, $y$, $\Pred_{px}\land 
       	\Pred_{{px,pxy}}\implies 
       	\Pred_{{s'\!,pxy}}$.

\TODO{We need to prove that we have the following  relation:}  \\     	
       	\begin{small}
 $\Pred_{s,u} \land \Pred_{OT}\\
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\!\!\bigvee_{y\in Y}\!\!\bigvee_{p\in P}
       		\left( \forall j. \vis{\beta_j}=\gamma_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
       		\land \alpha\!=\!\alpha_{pxy} \land
       		\Pred_{{s',\!xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)$.
       	\end{small}

\noindent By rule given in (2) we have for all $p$:\\
\begin{small}
$\big(\Pred_{s,p} \land \Pred_{OT}\big)\land\Pred_{p,u}\\
       		\hspace{1cm} \implies\!\!\! \Big(\bigvee_{x\in X}
       		\left( \forall j. \vis{\beta_j}=\gamma_{jpx}  \Rightarrow \Pred_{OT_{px}}
       		\land \alpha\!=\!\alpha_{px} \land
       		\Pred_{{s'\!,px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\Big)\land\Pred_{p,u}\\
       		%
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\!
       	\Big( \forall j.\vis{\beta_j}\!=\!\gamma_{jpx}  \Rightarrow 
       		(\Pred_{OT_{px}}\land\Pred_{p,u})
       		\land \alpha\!=\!\alpha_{px} \land
       		\Pred_{{s'\!,px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\Big).\\
       		%
       		$
  \end{small}

\noindent By rule given in (3) we have:   \\
$\Pred_{p,u} \land \Pred_{OT_{px}}\\
       	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
       	\left( \forall j. \gamma_{jpx}=\gamma_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
       	\land \alpha_{px}\!=\!\alpha_{pxy} \land
       	\Pred_{{px,pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$.\\

\noindent So can rewrite the formula as:\\	
\begin{small}
$ \big(\Pred_{s,p} \land \Pred_{OT}\big)\land\Pred_{p,u}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       	\bigg( \forall j.\vis{\beta_j}\!=\!\gamma_{jpx}  \Rightarrow\\~~\hspace{2em}
       		\Big(\!\bigvee_{y\in Y}
       			\left( \forall j'. \gamma_{j'px}\!=\!\gamma_{j'pxy}  \Rightarrow \Pred_{OT_{pxy}}\!\land \alpha_{px}\!=\!\alpha_{pxy}
\land \Pred_{{px,pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)   \Big)\\~~ \hspace{2em} \land \alpha\!=\!\alpha_{px} \land
       		\Pred_{{s'\!,px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\bigg).\\
\hspace{1cm}\implies\!\!\!\!\bigvee_{x\in X} \bigvee_{y\in Y}\bigg(\forall j, j'.\vis{\beta_j}\!=\!\gamma_{jpx}\!\land\!\gamma_{j'px}\!=\!\gamma_{j'pxy}
 \Rightarrow\\~~\hspace{2em} \Big(\Pred_{OT_{pxy}}\!\land\alpha\!=\alpha_{px}\!=\!\alpha_{pxy} \land 
       \Pred_{{px,pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}
       		\land
\Pred_{{s'\!,px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\Big)\bigg).
       		$
       \end{small}

\medskip
\noindent Because of variables domains independence we  have:\\ 
    $\Pred_{{s'\!,px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\land 
       	\Pred_{{px,pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}
       	\Leftrightarrow\\ % we changed =
\Pred_{{s'\!,px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\land
       \Pred_{{px,pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}} \Leftrightarrow
\big(\Pred_{{s'\!,px}} \land   \Pred_{{px,pxy}}\big)   \subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}} \\	\implies\Pred_{{s'\!,pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}
\subst{\Post_{OT_{pxy}}}\Leftrightarrow  \Pred_{{s'\!,pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}} $\\

\noindent This allows us to conclude with $\Pred_{s,u} = \bigvee_{p\in P} 
       	\Pred_{s,p}\land\Pred_{p,u}$:

      	\begin{small}     	
$\Pred_{s,u} \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{p\in P} \big(
	\Pred_{s,p}\land\Pred_{p,u}\big) \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\!\bigvee_{p\in P}\bigg(\!\!
 \bigvee_{x\in X}\!\!\bigvee_{y\in Y}\!\!
\Big( \forall j, j'.\vis{\beta_j}\!=\!\gamma_{jpx} \land \gamma_{j'px}\!=\!\gamma_{j'pxy}\Rightarrow\\~~\hspace{2em}
\Big( 
\Pred_{OT_{pxy}}
\land \alpha\!=\alpha_{px}\!=\!\alpha_{pxy} \land
\Pred_{{s'\!,pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\Big)\Big)\bigg)
\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\!\!\bigvee_{y\in Y}\!\!\bigvee_{p\in P}\!\!
\Big(\forall j.\vis{\beta_j}\!=\!\gamma_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
\land\, \alpha\!=\!\alpha_{pxy} \land
\Pred_{{s'\!,pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\Big)$.
  \end{small}
